---
title: "CIND110_Assignment2"
output: html_document
date: "2023-08-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 2

Install packages

```{r}
# Comment this before knitting
# install.packages("tm", dependencies = T)
# install.packages("RWeka", dependencies = T)
# install.packages("textstem", dependencies = T)
# install.packages("textclean", dependencies = T)
# install.packages("text2vec", dependencies = T)
```

## Question 2

Read the relational dataset, and apply three different text pre-processing techniques to cleanse the description attribute.

```{r}
# Loading packages to current workspace
lstPackages <- c('tm', 'RWeka', 'textstem', 'textclean', 'text2vec')
lapply(lstPackages, library, character.only = TRUE)
```


```{r}
# Load dataset
rawData <- read.csv(file = "Flowers_CSV_Data.csv", header = T, sep = ",")

# Read the dataset
numberOfDocs <- length(rawData$id)
rawData$id <- paste0("Doc", c(1:numberOfDocs))
rawData
```


```{r}
# Prepare the corpora
listOfDocs <- tm::VectorSource(rawData$description)
listOfDocs$Names <- names(rawData$id)
corporaData <- tm::VCorpus(listOfDocs)

```

Preprocessing technique 1: Stopword removal

```{r}
corporaData <- tm::tm_map(corporaData, removeWords, stopwords('english'))
corporaData <- tm::tm_map(corporaData, removeWords, stopwords('SMART'))
corporaData
```

Preprocessing technique 2: Stemming

```{r}
corporaData <- tm::tm_map(corporaData, stemDocument)
corporaData
```

Preprocessing technique 3: Removing punctuation marks

```{r}
corporaData <- tm::tm_map(corporaData, content_transformer(tolower))
corporaData <- tm::tm_map(corporaData, removePunctuation, ucp = T, 
                           preserve_intra_word_contractions = F,
                           preserve_intra_word_dashes = F)
corporaData
```

## Question 3 Create a unigram TermDocumentMatrix (TDM) and then represent it in a matrix format and display its dimension.

```{r}
# Create a uni-gram Term Document Matrix
term.doc.matrix.lg <- tm::TermDocumentMatrix(corporaData)
tm::inspect(term.doc.matrix.lg[1:10, 1:10])

# Represent TDM in a matrix format and display its dimensions
term.doc.matrix.unigram <- as.matrix(term.doc.matrix.lg)
dim(term.doc.matrix.unigram)
head(term.doc.matrix.unigram)
```


## Question 4 Using the vectors obtained in the previous question, apply the cosine similarity function and identify which flower is most similar to 'Rose'.

```{r}
# Reduce dimensions of TDM uni-gram matrix
term.doc.matrix.lg <- tm::removeSparseTerms(term.doc.matrix.lg, 0.8)
tm::inspect(term.doc.matrix.lg[1:10, 1:10])

# Represent the TDM as a regular matrix
term.doc.matrix.unigram <- as.matrix(term.doc.matrix.lg)
dim(term.doc.matrix.unigram)
head(term.doc.matrix.unigram)
```
```{r}
# Declaring weights (TF-IDF variants)
tf.idf.weights <- function(tf.vec){
  # Computes tfidf weights from term frequency vector
  n.docs <- length(tf.vec)
  doc.frequency <- length(tf.vec[tf.vec > 0])
  weights <- rep(0, length(tf.vec))
  relative.frequency <- tf.vec[tf.vec > 0] / sum(tf.vec[tf.vec > 0])
  weights[tf.vec > 0] <- relative.frequency * log10(n.docs/doc.frequency)
  return(weights)
}
```


```{r}
# Compute the TF-IDF (unigram)
tfidf.matrix.uni <- t(apply(as.matrix(term.doc.matrix.unigram), 1,
                            FUN = function(row) {tf.idf.weights(row)}))
colnames(tfidf.matrix.uni) <- rawData$id
head(tfidf.matrix.uni)
dim(tfidf.matrix.uni)
```

Doc0 is Rose so let's see which flower is most similar to Rose.

```{r}
# Compute Cosine similarity indices for the uni-gram TDM
c.similarity.matrix.uni <- text2vec::sim2(t(tfidf.matrix.uni), method='cosine')

# display ranked lists
sort(c.similarity.matrix.uni["Doc0",], decreasing = T)
```

```{r}
c.similarity.matrix.uni["Doc0",]
```

The Flower Rose is most similar to the 4th and 9th flower, Sunflower and Marigold.







